% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Ran Feng}

\basicInfo{
  \email{ranf@usc.edu} \textperiodcentered\ 
  \phone{(213)-284-2776} \textperiodcentered\ 
  \linkedin[ranf999]{https://www.linkedin.com/in/ranf999}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{University of Southern California}, Los Angeles, CA}{2016 -- Present}
\textit{Master student} in Computer Science(General), expected May 2018
\datedsubsection{\textbf{Sichuan University}, Chengdu, China}{2012 -- 2016}
\textit{B.S.} in Computer Science     GPA:3.6/4.0

\section{\faCogs\ Skill Highlights}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C/C++, Java, Python 
  \item Operatin System: Linux
  \item Web Development: SpringMVC, Mybatis, MySQL
  \item Other: Cocos2d-x Game Engine, Flink, Hbase, Vim, Git
\end{itemize}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Didi Chuxing} Beijing, China}{5/2017 -- 8/2017}
\role{Summer Intern}{Manager: Qiuye Zheng}
1.Development of Real-time multi-dimensional data analysis system
Brief introduction: Compute the real-time amount of orders of different user level and driver level in different city.
\role{Apache Flink, Hbase, Phoenix, Druid}
\begin{itemize}
  \item Implemented real-time stream data processing by Flink, joined the offline user and driver level data using Phoenix and Hbase, supported OLAP functions by Druid.
  \item The latency of stream data processing decreased over 25\%.
\end{itemize}

2.Tableau add-on functions development
Brief introduction: Automatically synchronize the Tableau workbooks, authorization and UV, PV data to the uniform report system in Didi Chuxing. Optimized data extraction scheduling for Tableau.
\role{SpringMVC, MySQL, RESTful API}
\begin{itemize}
  \item Using thread pool to control the threads for downloading workbooks and parsing workbooks metadata.
  \item Using Highest Response Ratio Next algorithm to adjust the priority of data extraction tasks.
  \item The average blocking time of data extraction tasks decreased 50\%.
\end{itemize}


\datedsubsection{\textbf{Weenix-Operating System}}{Jan. 2017 -- Apr. 2017}
\role{C, Linux}{Group Projects}
Brief introduction: Implemented three parts of an Unix-like operating system kernel – threads and processes, virtual file system(VFS) and virtual memory.
\begin{itemize}
  \item Implemented the process controller, thread queue, thread scheduler and synchronization primitives.
  \item Developed the functions and system calls of VFS and virtual memory management.
  \item Developed on Linux using C and debugging with GDB.
\end{itemize}

\datedsubsection{\textbf{Campus RPG Navigation Mobile Game Based on Cocos2d-x}}{Nov. 2013 -- Aug. 2015}
\role{C++, Cocos2d-x, JNI}{Group Projects, team leader}
Brief introduction: Designed an Mobile RPG game with concrete storyline to promote campus culture and guide first-year students around campus with real campus map and GPS navigation.
\begin{itemize}
  \item Implemented the physics engine, event trigger strategy, battle system, and GPS navigation module.
  \item Implemented communication between JAVA and C++ with JNI.
  \item 8000+ lines of code, published on Wandoujia(Chinese Largest Android AppStore) with 1000+ downloads, won the 1st Prize in Sichuan University Software Design Competition.
\end{itemize}

\datedsubsection{\textbf{Monitoring and Control System for Indoor Environment Based on Arduino}}{Jan. 2016 -- Apr. 2016}
\role{C, Java, Mybatis, Arduino}{Individual Project}
Brief introduction: Monitors indoor environment through various sensors and displays data on a web interface or an Android application.
\begin{itemize}
  \item Developed an Arduino module for each environment sensor, wrote the network transmission program and transmitted data through GPRS using SIM908 module.
  \item Using Jsp+Servlet+Mybatis framework and MySQL database. Developed Android WebApp.
  \item Outstanding undergraduate graduation design.
\end{itemize}

\datedsubsection{\textbf{\LaTeX\ résumé template}}{May. 2015 -- Present}
\role{\LaTeX, Maintainer}{Individual Projects}
An elegant \LaTeX\ résumé template, https://github.com/billryan/resume
\begin{itemize}
  \item Easy to be further customized or extended
  \item Full support for unicode characters (e.g. CJK) with \XeLaTeX\
  \item FontAwesome 4.5.0 support
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
